Big data' og politologisk datavidenskab

### 2020-03-11 draft_v01.Rmd
some more structure

@@

- Pattern discovery (dimensionality reduction -- a la argument in Lowe 2013WP)
  - Generic data: Clustering, IRT, etc.
  - Text: Topic modeling, text scaling, dictionaries
  - Fundamental unity of goals and approach
  - Variety in methods results from variation in:
    - Assumptions re: underlying model/geometry of latent space
    - Related to above: something like, "format" of output
    - Structure/nature of input data
    - Amount of domain expertise applied to structure results
    - Assumptions about what is correlated with what
    - Level of computational intensity

>>>>

- Definition of machine learning: "y-hat vs. beta-hat"

@@

- Getting data: scraping, APIs, text databases

- Pattern discovery (dimensionality reduction -- a la argument in Lowe 2013WP)
  - Generic data: Clustering, IRT, etc.
  - Fundamental unity of goals and approach
  - Variety in methods results from variation in:
    - Assumptions re: underlying model/geometry of latent space
    - Related to above: something like, "format" of output
    - Structure/nature of input data
    - Amount of domain expertise applied to structure results
    - Assumptions about what is correlated with what
    - Level of computational intensity

- Text: Topic modeling, text scaling, dictionaries
